\documentclass[11pt]{scrartcl}
\usepackage[left=1.1in,right=1.1in]{geometry}
\usepackage{sprint}
\usepackage[toc]{glossaries}
\newglossary[alg]{amanda}{ald}{adn}{Glossary}
\newglossary[blg]{animals}{bld}{bdn}{Glossary}


\rhead{\textsf{ENGLISH NOTES}} %Rightside
\lhead{\textbf{Pragyan Pranay}} %Leftside

\makeglossaries

\loadglsentries{Glossary amanda.tex}
\loadglsentries{Glossary-Animals.tex}


\begin{document}
    \title{English Term-2 Poems}
    \author{Pragyan Pranay}
    \date{24 January, 2022}
 \maketitle

\tableofcontents


\section{Amanda}
This poem is all about a child like me ranting about how 
parents are always acting around boss and bullying us 
every time about not studying and commanding and controlling 
us in such a manner that we feel so irritated and lost that 
we get the inspiration to write this poem. 

This poem is written by \textbf{Robin Klein} and has a total
of 7 paragraphs or whatever. The paragraphs alter between 
imagination of Amanda and her mother's scoldings.

\vspace{4mm}

\noindent \textbf{Paragraph 1:} In the first paragraph, we 
see Amanda's
mother telling her \textit{not to }
\begin{itemize}
    \item bite her nails
    \item \gls{hunch} her shoulders
    \item to stop \gls{slouching} and sit straight up
\end{itemize}

\noindent \textbf{Paragraph 2:} Here she is imagining that 
she is a mermaid who is in a \gls{emerald} coloured \gls{languid} sea 
who is moving around \gls{blissfully}.

\vspace{4mm}

\noindent \textbf{Paragraph 3:} This is time for homework 
which is one of the most annoying things to a child. Later 
she asked her if she had cleaned her room and cleaned her 
shoes or not.

\vspace{4mm}

\noindent \textbf{Paragraph 4:} IMAGINATION! This one is 
quite interesting. She said here that she is an orphan which 
is clearly not true. She is trying to make patterns in the 
soft dust with her \textit{\gls{hushed}, bare feet}. Another 
thing to notice is that she is thinking the opposite of her 
mother. At one side, her mother wants her to keep herself tidy 
and well-arranged whereas Amanda wants to play in the dust, 
without any worries.She also compliments silence as 
``golden" and freedom as ``sweet''. Very ordinary stuff after 
the constant \textit{nagging} by parents.

\vspace{4mm}

\noindent \textbf{Paragraph 5:} Don't eat chocolate because 
of cavities and more importantly as a growing child, you do 
have to face acne. Also, always look at your parents when 
they are talking to you.

\vspace{4mm}

\noindent \textbf{Paragraph 6:} She is in another world 
right now. She says that she is Rapunzel and she does not 
about all the worldly affairs. She finds her life \gls{tranquil} 
in her own dream world. She also denies Rapunzel's idea 
of letting her hair down and escaping the tower and values 
the calmness in the tower.

\vspace{4mm}

\noindent \textbf{Paragraph 7:} Mother starts again! Her 
mother says that Amanda was moody and said her to 
stop \gls{sulking}. She said that the way she was behaving, people 
would think that Amanda was \gls{nagged} by her mother. Poor little 
Amanda couldn't even say that it was indeed the case!

\printglossary[type=amanda]

\section{Animals}
This chapter is about a depressed guy who is too weak to live 
in this world and says that he wants to live with animals, where 
there is no competition, and everything is peaceful. He will 
continuously say that animals are very good and they do not 
complaint about their situations no matter what happens. He 
feels very comfortable with those animals who stay as who they 
are without acting and giving false impressions. This basically 
means that he is fed up with life and wants to go to Himalayas 
and leave all the false people in the world.

\vspace{3mm}

This poem is written by Walt Whitman who is said to be a very 
nice and well-known poet. This poem is of about 4 paragraphs 
where the last paragraph is short and concludes the poem. I 
do oppose the poet at several points, but I do get how he feels.
Let us begin.

\vspace{4mm}

\noindent \textbf{Paragraph 1:} He introduces us the notion 
of living with animals and starts to appreciate them. He tells 
everyone that animals are so \gls{placid} to live with. They are 
also self contain'd which means that they are happy and never 
interfere with other's life. He keeps gazing at those lovely 
animals admiring the animals.

\vspace{3mm}

\noindent \textbf{Paragraph 2 \& 3:} The poet here tell us about 
how animals live and what actually attracts him. Some things 
which is written in the textbook are:
\begin{itemize}
    \item They don't sweat and \gls{whine} about their condition. 
    \item They never lie awake in dark and weep about their sins. 
    \item Animals don't make the people sick by discussing their duty to god.
    \item Everybody is self-contained and is not obsessed with the mania of owning things.
    \item There is no respect for those who have lived for a longer age and is everyone is equal. Nobody kneels to each other.
    \item There is no one who is respectable or unhappy over the earth.
\end{itemize}
The poet addresses the fact that he feels that he had all 
qualities once in him.

\vspace{3mm}

\noindent \textbf{Paragraph 4:} In the last paragraph, he 
refers all the good qualities of a person as some tokens. He 
says that the humans might have dropped them a long back ago 
negligently. It could include qualities such as kindness, 
honesty, sympathy, and contentment. These tokens were then 
probably picked up by animals making them what he sees them as.

\printglossary[type=animals]
\newpage

\section{The Tale of Custard the Dragon}
This poem is quite amusing but lengthy at the same time with 
15 stanzas. We are not going to go through each of them
but will rather try to give the main points. The poet of the 
poem is \emph{Ogden Nash}. It is about a dragon who people 
teased to be very coward and a scaredy-cat who heroically 
saves everyone time of danger.

\vspace{4mm}

\begin{question}
    Who lived in the White House?
\end{question}
\begin{ans}
    Belinda lived with her pets in the White House. She had 
    a little black cat, a yellow dog, a little grey mouse and a real 
    dragon as a pet! Not to forget, she had a red wagon too.
\end{ans}
\begin{question}
    What and why did Belinda name her pets?
\end{question}
\begin{ans}
    Belinda named her pets like
    \begin{itemize}
        \item Little Black Cat: Ink
        \item Little Grey Mouse: Blink
        \item Yellow Dog: Mustard
        \item The Coward Dragon: Custard
    \end{itemize}
    The reason for their names are obvious.
\end{ans}
\begin{question}
    Describe the appearance of Custard.
\end{question}
\begin{ans}
    Custard was a dragon who had spikes on the top him and 
    scales underneath. He also had big sharp teeth. His nose 
    was more like a fireplace or a chimney because of the fire 
    he breaths. Custards toes were no less than sharp daggers.
\end{ans}
\begin{question}
    Give a character-sketch of all the pets of Belinda.
\end{question}
\begin{ans}
    We just split this into points:
    \begin{itemize}
        \item Custard was really coward dragon who wanted a nice safe cage. 
        \item On the other hand, Mustard was a really brave dog. He was as brave as a lion in rage.
        \item Ink and Blink could chase lions down the stairs!
    \end{itemize}
    This tells everyone except Custard were very courageous.
\end{ans}
\begin{question}
    How did they treat Custard?
\end{question}
\begin{ans}
    Custard was teased quite badly. He was tickled mercilessly 
    by Belinda and was often called \emph{Percival}. They all 
    sat laughing seeing the pathetic condition of Custard. Ink 
    and Blink rudely used to ask his age to tease him again.
\end{ans}
\begin{question}
    Describe the appearance of the Pirate.
\end{question}
\begin{ans}
    The pirate had pistols in both of his hands. He had a cutlass 
    bright in his teeth. He also had a black beard one leg was 
    wooden.
\end{ans}
\begin{question}
    How did everyone react when the Pirate entered?
\end{question}
\begin{ans}
    Everyone was frightened. Belinda cried for help, Mustard fled 
    from the situation, Ink ran away and hid in bottom of the 
    household. Blink strategically hid in his mouse hole.
\end{ans}

\end{document}